Introduction to Natural Language Processing

### 2007-07-12 slides/baypiggies.tex
incomplete slides on RTE
svn/trunk@4871

>>>>

\begin{frame}
  \frametitle{NLP}

\begin{block}{Major sub-domains of NLP}
  \begin{itemize}
    \item Understanding
    \item Translation
    \item Generation
  \end{itemize}
\end{block}

\begin{block}{Modalities}
  \begin{itemize}
    \item Text
    \item Speech
    \item Images
  \end{itemize}
\end{block}

\end{frame}

\begin{frame}
  \frametitle{Textual Inference}

\begin{exampleblock}{Example 1}
  \begin{description}
    \item [Text] Never before had ski racing, a sport dominated by
      monosyllabic mountain men, seen the likes of Alberto Tomba, the
      flamboyant Bolognese flatlander who at 21 captured two gold
      medals at the Calgary Olympics.
    \item [Hypothesis] Alberto Tomba won a race.
  \end{description}
\end{exampleblock}

\end{frame}

\begin{frame}
  \frametitle{Textual Inference}

\begin{exampleblock}{Example 2}
  \begin{description}
    \item [Text] Researchers at the Harvard School of Public Health
      say that people who drink coffee may be doing a lot more than
      keeping themselves awake---this kind of consumption apparently
      also can help reduce the risk of diseases.
    \item [Hypothesis] Coffee drinking has health benefits.
  \end{description}
\end{exampleblock}

\end{frame}

\begin{frame}
  \frametitle{Why is it useful?}

  \begin{description}
    \item[Information Extraction] 
    \item[Spoken Dialogue] 
    \item[Question Answering] Who won races at the Calgary Olympics?
    \item[Text Summarization] 
  \end{description}

\end{frame}
